Higher-Order unification for free!

### 2024-04-13 paper/main.tex
sec 3.4 with spellchecker

A step in \Ho consists in unifying two terms and reconsidering all
links for progress. If any of the two tasks fails we say that the entire step
fails, and it is at this granularity that we can relate steps in the
two languages.

@@

\noindent
Note tha the infix notation \elpiIn{((A ~\Ue~B) C D)} is syntactic sugar for
\elpiIn{((~\Ue\!\!\!~) A B C D)}.

Reconsidering links is a fixpoint, since the progress of a link can update the
substitution and in turn enable another link to progress.

@@

\subsubsection{Progress}
In the base compilation scheme \elpiIn{progress1} is the identity
on both the links and the substitution, so the fixpoint trivially terminates.
Sections \ref{sec:eta} and \ref{sec:beta} add rules to \elpiIn{progress1}
and justify why the don't hinder termination.
% For brevity we omit the code
% that applies the substitution \elpiIn{S1} to all terms in \linkStore.

\subsubsection{Occur check}\label{sec:oc}
Since compilation moves problematic terms out of the sight of \Ue{},
that procedure can only perform a partial occur check. For example the
unification problem $X \Ue f~Y$ cannot generate a cyclic substitution alone,
but should be disallowed if a $\linkStore$ contains a link like
$\linketaM{}{Y}{\lambda z.X_z}$: we don't know yet if $Y$ will feature
a lambda in head position, but we surely know it contains $X$, hence
$f~Y$ and that fails the occur check.
The procedure \elpiIn{occur-check-links} is in charge of
performing this check that is needed in order to
guarantee \fullref{prop:fidelity}.

>>>>

A step in \Ho consists of unifying two terms and reconsidering all
links for progress. If either of these tasks fails, we consider the entire step to
fail. It is at this granularity that we can relate steps in the
two languages.

@@

\noindent
Note that the infix notation \elpiIn{((A ~\Ue~B) C D)} is syntactic sugar for
\elpiIn{((~\Ue\!\!\!~) A B C D)}.

Reconsidering links is a fixpoint process because the progress of a link
can update the substitution, which may then enable another link to progress.

@@

\subsubsection{Progress}
In the base compilation scheme, \elpiIn{progress1} is the identity function
on both the links and the substitution, so the fixpoint trivially terminates.
Sections \ref{sec:eta} and \ref{sec:beta} add rules to \elpiIn{progress1}
and explain why the don't hinder termination.
% For brevity we omit the code
% that applies the substitution \elpiIn{S1} to all terms in \linkStore.

\subsubsection{Occur check}\label{sec:oc}
Since compilation moves problematic terms out of the sight of \Ue{},
that procedure can only perform a partial occur check. For example, the
unification problem $X \Ue f~Y$ cannot generate a cyclic substitution alone,
but should be disallowed if a $\linkStore$ contains a link like
$\linketaM{}{Y}{\lambda z.X_z}$: we don't know yet if $Y$ will feature
a lambda in head position, but we surely know it contains $X$, hence
$f~Y$ and that fails the occur check.
The procedure \elpiIn{occur-check-links} is in charge of
performing this check that is needed in order to
guarantee \fullref{prop:fidelity}.
